# Dosen {#intro}

Saat ini Universitas Sultan Ageng Tirtayasa memiliki 619 dosen PNS. Dosen PNS di Universitas Sultan Ageng Tirtayasa tersebar di 6 Fakultas, di antaranya:

* Fakultas Hukum (52)
* FKIP (174)
* Fakultas Teknik (138)
* Fakultas Pertanian (70)
* Fakultas Ekonomi dan Bisnis (109)
* FISIP (57)
* Fakultas Kedokteran (19)

Sebaran lengkap dosen PNS Universitas Sultan Ageng Tirtayasa di tiap fakultas bisa dilihat pada diagram berikut.

```{r, echo=FALSE}
dosen <- read.csv("static/dosen.csv", sep = ";")
dosen <- dosen[, 1:9]
library(ggplot2, warn.conflicts = F)
library(dplyr, warn.conflicts = F)
library(plotly, warn.conflicts = F)
plot_ly(dosen, x = ~FAKULTAS) %>%
  add_histogram()
```

Berikut adalah sebaran dosen PNS Universitas Sultan Ageng Tirtayasa berdasarkan jenis kelamin.

```{r, echo=FALSE}
jk <- dosen %>%
  group_by(JK) %>%
  summarize(banyak = n())

plot_ly(type = "pie", labels = jk$JK, values = jk$banyak,
        textinfo = "label+percent",
        insidetextorientation = "radial")
```


Berikut adalah sebaran dosen PNS Universitas Sultan Ageng Tirtayasa berdasarkan tingkat pendidikan.

```{r, echo=FALSE}
pendidikan <- dosen %>%
  group_by(PENDIDIKAN) %>%
  summarize(banyak = n())

plot_ly(type = "pie", labels = pendidikan$PENDIDIKAN, values = pendidikan$banyak,
        textinfo = "label+percent",
        insidetextorientation = "radial")
```

Berikut adalah sebaran dosen PNS Universitas Sultan Ageng Tirtayasa berdasarkan golongan.

```{r, echo=FALSE}
plot_ly(dosen, x = ~GOL) %>%
  add_histogram()
```

Berikut adalah sebaran dosen PNS Universitas Sultan Ageng Tirtayasa berdasarkan jabatan akademik.

```{r, echo=FALSE}
jabatan <- dosen %>%
  group_by(JABATAN) %>%
  summarize(banyak = n())

jabatan$JABATAN <- c("Asisten Ahli", "Guru Besar", "Lektor",
                     "Lektor Kepala", "Tenaga Pengajar")

plot_ly(type = "pie", labels = jabatan$JABATAN, values = jabatan$banyak,
        textinfo = "label+percent",
        insidetextorientation = "radial")
```

Berikut adalah daftar nama dosen PNS di Universitas Sultan Ageng Tirtayasa.

```{r, echo=FALSE}
DT::datatable(dosen[,c(1, 3, 4, 7:9)])
```



You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
